Predicting computational reproducibility of data analysis pipelines \\in large population studies using collaborative filtering

### 2018-07-26 paper.tex
Finished discussion on overlap matrix

Figure~\ref{fig:overlap} illustrates the comparison between RFNU, RFNTL 
and RFNTS. The matrices in this Figure represent the union between the 
training and the test set, where the training set is represented in 
black (negatives) and white (positives), and the test set is 
represented in green (true positives), yellow (false negatives), gray 
(true negatives) and red (false positives). This representation 
provides insights regarding where, and perhaps why, prediction errors 
occur. At this training ratio, RFNU (Figure~\ref{fig:overlap-rfntu}) 
uniformly samples the number of files per subject between 0.8$N_f$ and 
$N_f$. It provides an opportunity for ALS to be trained on the last 
files of the pipelines, while maintaining a low number of columns with 
a low training ratio. On the contrary, RFNTL 
(Figure~\ref{fig:overlap-rfntl}) samples the number of files per 
subject from 0.85$N_f$, but the probability to have a complete column 
is 0 (the one complete column in Figure~\ref{fig:overlap-rfntl} is the one included
to prevent cold start issues).

>>>>

Figure~\ref{fig:overlap} illustrates the comparison between RFNU, RFNTL 
and RFNTS. The matrices in this Figure represent the union between the 
training and the test set, where the training set is represented in 
black (negatives) and white (positives), and the test set is 
represented in green (true positives), yellow (false negatives), gray 
(true negatives) and red (false positives). This representation 
provides insights regarding where, and perhaps why, prediction errors 
occur. At this training ratio, RFNU (Figure~\ref{fig:overlap-rfntu}) 
uniformly samples the number of files per subject between 0.8$N_f$ and 
$N_f$. It provides an opportunity for ALS to be trained on the last 
files of the pipelines, while maintaining a low number of columns with 
a low training ratio. On the contrary, RFNTL 
(Figure~\ref{fig:overlap-rfntl}) samples the number of files per 
subject from 0.85$N_f$, but the probability to have a complete column 
is 0 (the one complete column in Figure~\ref{fig:overlap-rfntl} is the 
one included to prevent cold start issues), which leads to a "stripe" 
of errors at the bottom of the matrix. RFNTS 
(Figure~\ref{fig:overlap-rfnts}) doesn't have this issue, as it 
includes many complete columns in the training set, but this comes at 
the cost of several columns with a very low number of files, lower than 
60\%. For such columns, the prediction may go somewhat wrong, which explains
the reduced accuracy compared to RFNU.
